\documentclass[10pt,letterpaper]{letter}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
Welcome everyone and thank you for joining us today.   I'm honored to be the graduate speaker for today's convocation ceremony.  And a heartfelt thank you to the staff and faculty of the electrical and computer engineering department for all their support through my PhD program, and the computer science department for my master's degree.  I'd especially like to thank my PhD advisor, Greg Heileman, my Master's advisor, George Luger, and especially my wife for her support throughout the years.

When I started working on my PhD, I had a nice full head of hair.  That gives you some idea of how long I've been here.  As I expect a few of you may pursue graduate degrees or continue to extend your programs into PhDs, I thought I'd spend a few minutes going over a few of the things I've learned in my very, very long career as a student.

First, don't have kids until you're finished with graduate school. Despite what you might think, sleeping in 1 to 2 hour chunks because your kid, say, tried green chile that day, watched some scary elmo episode, or whatever really isn't that cool.  And it really doesn't help you focus the next day, despite what you might think.  Now, granted, because you're up a 5AM just about every day, you'll never be late because you're sleeping in.  You'll be late because your kids hid your shoes.  And they think that's hilarious.

Second, don't work a full time job while you're trying to finish your degree either.  Find something part time, something through the department, and something at least close to what you plan to do when you escape graduate school.  Working full time while going finishing a graduate degree great if you're studying the effects of sleep deprivation.  On yourself.  The thing is that you're too tired to notice any of the effects anyway.  And believe me, the quality of code you write in those hours between 12AM and 6AM, the time you'll have left to take care of school work after your full time job, is not precisely fabulous.

If you're going to work full time and finish your graduate degree though, make sure you do get married and have a family.  That way, all the money from your full time job will go to your kids, and you'll still get to enjoy the poor graduate student experience to its fullest.

Now, I know, with all these clear advantages, there was really no way I could end up washing out.  But I really did pick up one thing that I think really made the difference, for me at least.  Now I wasn't the smartest graduate student in the program, and though I have a decent CV at this point, other students have published stronger work than I have.  I've had many a paper I've submitted rejected too.  But the only thing that really got me up here today was that I just didn't quit.  I'd get plenty frustrated, believe me, especially after some of those not-so-friendly paper reviews.  Or after bombing an exam.  Or after I crawled out of bed at 4AM for the third night in a row after a couple hours sleep to try to get something done on my dissertation while everybody else was sleeping.  But I figured out that all that was okay.  I just needed the grit to keep moving forward, to keep going to class, to keep writing, to keep working.  As long as I kept it up, I knew I'd finish one day.  Even if the department let me graduate because they were tired of seeing me around the place.

I was lucky, I knew I wanted a PhD, and I knew what I wanted it for.  I wanted to learn how to find new problems, and figure out how to solve them.  I wanted to know how to really contribute and be a part of the conversation, how to, maybe if I was lucky, find the right problem to work on that could help make the world slightly better after I was in it.  And if that's something that sounds good to you, if that's something you'd like to do too, listen to yourself like I did, figure out what's really important to you, and get started.  And don't quit.

Thank you.
\end{document}